\documentclass[11pt, a4paper, twocolumn]{jsarticle}
%
\usepackage{amsmath,amssymb}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{ascmac}
\usepackage{subfigure}
\usepackage{multicol}
\usepackage{setspace}
\usepackage{url}
%
\setlength{\textwidth}{\fullwidth}
\setlength{\textheight}{39\baselineskip}
\addtolength{\textheight}{\topskip}
\setlength{\voffset}{-0.5in}
\setlength{\headsep}{0.3in}
%
\renewcommand{\baselinestretch}{1.0}
\renewcommand{\figurename}{Fig.}
\renewcommand{\tablename}{Table.}
\renewcommand{\headfont}{\bfseries}


\begin{document}
\twocolumn[
\begin{screen}
\begin{flushleft}
融合情報学輪講資料\hspace{\fill}2013/12/6
\end{flushleft}
\begin{center}
{\Large  Multipath TCPによるデータセンターネットワークの改善  \\
Improving the datacenter network with Multipath TCP}
\end{center}
\begin{flushleft}
工学系研究科 電気系工学専攻 関谷研究室\hspace{\fill}修士課程1年 37-136482 藤居 翔吾
\end{flushleft}
\end{screen}
]

\begin{spacing}{0.7}
\begin{bfseries}
\begin{itshape}
Abstract-
\end{itshape}
In accordance the explosive growth of smartphone users, Web access based on
HTTP/TCP using a Web browser has become an indispensable service.
The performance of web browsing depends on the aepect of hardware and software.
In order to achieve the speeding up of web access, a lot
pf paper are written.
However, there are a few researches for reducing the number of HTTP transactions
to achieve shorter response time.

In this paper, the researches for reducing the response time are summarized and
introduced.
The response time of HTTP pipeline and Server Push in SPDY is compared by
calculating the number of transactions.
By the calculation, this paper concludes that SPDY achieve the fastest web
access compared with HTTP pipeline.
Some speeding up teqniques of Web access are introduced.
The page-loading time can be shortened by about a third.\\

\begin{itshape}
Index-
\end{itshape}
HTTP pipeline, Server Push, SPDY, Web access, Speeding-up, Round trips
\end{bfseries}
\end{spacing}
\section{Introduction}
ここ十年で, Webは私たちの生活に必要不可欠なものになった.


\end{document}